Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-22 paper/main.tex
natural transform

The continuity of the graphic is encapsulated as a category $\mathcal{\mathcal{\gbase}}$ containing open set objects $\opensetg$, the complete set of opensets $\gbase$ that is the full space of the graphic, and the empty set. As with $\mathcal{\dbase}$, the morphisms between the open sets  $\opensetg$ are inclusion morphisms $\iota$. Over the graphic space $\opensetg \subseteq \gbase$ are a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
  \{\gsectionc^{i}:\opensetgc_i\rightarrow \gtotalc\}|_{i\in I}
\end{equation}
which are the set of all graphics with a shared base space and fiber and are a subcategory of \textbf{Set}. This allows us to represent the full space of graphics as a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}
    {Ob(\bm{Set}) \ni \Gamma(\opensetgc_i, \gtotalc)}                                                                                                  &  & \{\gsectionc^{j}:\opensetgc_i\rightarrow \gtotalc\}|_{j\in J} \arrow[ll, "\iota"', hook'] \\ &  & \\
    \opensetgc_i \arrow[uu, "\sheafc(\gtotalc)"] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheaf_{\vartist}(\dtotalc)" description, dashed] &  & 
    \end{tikzcd}
\end{equation}
The set of graphics reachable through an artist function is a subset $\{\gsection^{j}\}|_{j\in J}$ of the full set of graphics. These sets of reachable graphics over opensets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf $\sheaf_{\vartist}$ from the graphic base space to the set of reachable graphics.

To establish a mapping between graphic and data base spaces, we introduce the surjective map $\vindex: \gtotal \rightarrow \dtotal$. Given the morphism $\iota$
\begin{equation}
  \label{eq:artist:vindex}
  \begin{tikzcd}
    & \opensetgc_i \arrow[d, "\iota"] \\
  \dbasec \arrow[ru, "\vindexc^*", dashed] & \gbasec \arrow[l, "\vindexc"]   
\end{tikzcd}
\end{equation}
we propose that a pushforward functor $\vindex_*$ 
\begin{equation}
  \vindexc_{*}:\mathcal{\dbasec} \rightarrow \mathcal{\gbasec}
\end{equation}
can be used to map between open sets $\openset_i \subset \dbase$ in data space and the open sets in visual space $\opensetg_i \subset \gbase$.

@@

We compose the functor $\vindex_*$ with the sheaf $\sheaf$ to move the sets of sections from $\Gamma(\openset, \dtotal)$ to $\Gamma(\opensetg, \vindex_* \dtotal)$. As illustrated in \autoref{fig:artist:pushforward_xi}, this operation copies a section and a fiber over one point $\dbasepoint \in \dbase$ such that it repeats over the corresponding region $\gbasepoint \subset \gbase$ in the graphic space.

>>>>

The continuity of the graphic is encapsulated as a category $\mathcal{\mathcal{\gbase}}$ containing open set objects $\opensetg$, the complete set of opensets $\gbase$ that is the full space of the graphic, and the empty set. As with $\mathcal{\dbase}$, the morphisms between the open sets  $\opensetg$ are inclusion morphisms $\iota$. Over the graphic space $\opensetg \subseteq \gbase$ are a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
  \{\gsectionc^{i}:\opensetgc_i\rightarrow \gtotalc\}|_{i\in I}
\end{equation}
which are the set of all graphics with a shared base space and fiber and are a subcategory of \textbf{Set}. This allows us to represent the full space of graphics as a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}
    {Ob(\bm{Set}) \ni \Gamma(\opensetgc_i, \gtotalc)}                                                                                                  &  & \{\gsectionc^{j}:\opensetgc_i\rightarrow \gtotalc\}|_{j\in J} \arrow[ll, "\iota"', hook'] \\ &  & \\
    \opensetgc_i \arrow[uu, "\sheafc(\gtotalc)"] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheaf_{\vartist}(\gtotalc)" description, dashed] &  & 
    \end{tikzcd}
\end{equation}
The set of graphics reachable through an artist function is a subset $\{\gsection^{j}\}|_{j\in J}$ of the full set of graphics. These sets of reachable graphics over opensets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf $\sheaf_{\vartist}$ from the graphic base space to the set of reachable graphics.

To establish a mapping between graphic and data base spaces, we introduce the surjective map $\vindex: \gtotal \rightarrow \dtotal$. Given the morphism $\iota$
\begin{equation}
  \label{eq:artist:vindex}
  \begin{tikzcd}
    & \opensetgc_i \arrow[d, "\iota"] \\
  \dbasec \arrow[ru, "\vindexc^*", dashed] & \gbasec \arrow[l, "\vindexc"]   
\end{tikzcd}
\end{equation}
we propose that a pushforward functor $\vindex_*$ 
\begin{equation}
  \vindexc_{*}:\mathcal{\dbasec} \rightarrow \mathcal{\gbasec}
\end{equation}
can be used to map between open sets $\openset_i \subset \dbase$ in data space and the open sets in visual space $\opensetg_i \subset \gbase$. We can then compose the functor $\vindex_*$ with the sheaf $\sheaf(\dtotal)$ 
\begin{equation*}
\vindex_*(\openset) \rightarrow \Gamma(\vindex_*(\openset), \vindex_* \dtotal) \coloneqq \opensetg \rightarrow \gamma(\opensetg, \vindex_* \dtotal) 
\end{equation*}
which allows for moving the sets of sections from $\Gamma(\openset, \dtotal)$ to $\Gamma(\opensetg, \vindex_* \dtotal)$. We denote the pulled forward sheaf as $\sheaf_{\vindex_*}(\dtotal)$.

@@

As illustrated in \autoref{fig:artist:pushforward_xi}, this operation copies a section and a fiber over one point $\dbasepoint \in \dbase$ such that it repeats over the corresponding region $\gbasepoint \subset \gbase$ in the graphic space. The pull forward functor allows us to formulate the data sheaf as 
\begin{equation}
  \label{eq:artist:data_pushforward_sheaf}
  \sheaf_{\vindex_*}: \mathcal{\gbase^{op}} \rightarrow \bm{Set}
\end{equation}

Following from \autoref{eq:artist:data_pushforward_sheaf} and the construction of the artist sheaf in \autoref{eq:artist:artist_sheaf}, we propose that the artist function $\vartist$ is a natural transformation

\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten=1.25em] & \\
\mathcal{\gbasec}^{op} \arrow[rr, "\sheafc(\dtotalc)", bend left] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right] &  & \textcolor{section}{\bm{Set}}\\
    & {} &                            
\end{tikzcd}
\end{equation}
